Optimal (Multiway) Spatial Joins

### 2024-06-01 msj.tex
yufei

>>>>

Finally, we generate, for each $h$, its set $\contained_R(h)$ (i.e., the set of rectangles covering $h$), where the rectangles $r$ are sorted by $\xright(r)$. To start with, initialize an empty linked list for every $h \in H$. Inspect the pairs $(h, \lambda) \in L$ in ascending order of the ID-field $\lambda$. For each pair $(h, \lambda)$ examined, identify the rectangle $r$ whose ID is $\lambda$ and add $r$ to the linked list of $h$. By the way the rectangle IDs were generated, it is clear that $\xright(r)$ is larger than or equal to the x-coordinates of the right edges of the rectangles already in the linked list. The whole scan over $L$ finishes in $O(1 + \out)$ time, and produces the correct output for Problem $\mathscr{E}$.
